Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/appendix.tex

Our last example is one which generates a trie intermediate data structure.

@@

We stage this algorithm by saying that the word set comes at stage \bbone\
and the query string comes at stage \bbtwo.

\begin{lstlisting} 
atsignmono { 
datatype letter = A | B | C 
datatype string = EmptyS | ConsS of letter * string
datatype list   = EmptyL | ConsL of string * list

@@

fun exists (mono{EmptyL},next{s}) = next{false} 
  | exists (mono{ConsL ht},next{s}) = 
	let atsignmono{
	  val (anyEmpty,a,b,c) = partition (ConsL ht)
	} in next { 
	case s of 
	  EmptyS2 => prev{hold mono{anyEmpty}} 
	| ConsS2 (A2,z) => prev{exists(mono{a},next{z})} 
	| ConsS2 (B2,z) => prev{exists(mono{b},next{z})}
	| ConsS2 (C2,z) => prev{exists(mono{c},next{z})}  
	} 
\end{lstlisting}

\noindent
Running the splitting algorithm on this code produces:

\begin{lstlisting}

datatype trie = Leaf 
			  | Branch of bool * trie * trie * trie

>>>>

Our last example generates a trie intermediate data structure.

@@

We stage this algorithm by saying that the word set comes at stage \bbone\
and the query string comes at stage \bbtwo.
\begin{lstlisting} 
atsignmono { 
datatype letter = A | B | C 
datatype string = EmptyS | ConsS of letter * string
datatype list   = EmptyL | ConsL of string * list

@@

fun exists (mono{EmptyL},next{s}) = next{false} 
  | exists (mono{ConsL ht},next{s}) = 
	let atsignmono{
	  val (anyEmpty,a,b,c) = partition (ConsL ht)
	} in next { 
	case s of 
	  EmptyS2 => prev{hold mono{anyEmpty}} 
	| ConsS2 (A2,z) => prev{exists(mono{a},next{z})} 
	| ConsS2 (B2,z) => prev{exists(mono{b},next{z})}
	| ConsS2 (C2,z) => prev{exists(mono{c},next{z})}  
	} 
\end{lstlisting}
Running the splitting algorithm on this code produces:
\begin{lstlisting} 
datatype trie = Leaf 
			  | Branch of bool * trie * trie * trie
